---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.align = "center",
  fig.path = "man/figures/README-"
)
```

<!-- badges: start -->
<!-- badges: end -->

# Overview

**MPWR** is an R package for multivariate time series (or multivariate 
structured longitudinal data) modeling and optimal segmentation via multiple 
polynomial piecewise regression (MPWR). It uses MLE for the estimation of the 
regression parameters with dynamic programming for the segmentation.

# Installation

You can install the MPWR package from [GitHub](https://github.com/fchamroukhi/MPWR_r)
with:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/MPWR_r")
```

To build *vignettes* for examples of usage, type the command below instead:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("fchamroukhi/MPWR_r", 
                         build_opts = c("--no-resave-data", "--no-manual"), 
                         build_vignettes = TRUE)
```

Use the following command to display vignettes:

```{r, eval = FALSE}
browseVignettes("MPWR")
```

# Usage

```{r, message = FALSE}
library(MPWR)
```

```{r, message = FALSE}
# Application to a toy data set
data("toydataset")
x <- toydataset$x
Y <- as.matrix(toydataset[,c("y1", "y2", "y3")])

K <- 5 # Number of segments
p <- 3 # Polynomial degree

mpwr <- fitMPWRFisher(X = x, Y = Y, K, p)

mpwr$summary()

mpwr$plot()
```

```{r, message = FALSE}
# Application to a real data set (human activity recogntion data)
data("realdataset")

x <- realdataset$x
Y <- as.matrix(realdataset[,c("y1", "y2", "y3")])

K <- 5 # Number of segments
p <- 3 # Polynomial degree

mpwr <- fitMPWRFisher(X = x, Y = Y, K, p)

mpwr$summary()

mpwr$plot()
```
