---
title: "A-quick-tour-of-MPWR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-quick-tour-of-MPWR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(
	fig.align = "center",
	fig.height = 5.5,
	fig.width = 6,
	warning = FALSE,
	collapse = TRUE,
	dev.args = list(pointsize = 10),
	out.width = "90%",
	par = TRUE
)
knit_hooks$set(par = function(before, options, envir)
  { if (before && options$fig.show != "none") 
       par(family = "sans", mar = c(4.1,4.1,1.1,1.1), mgp = c(3,1,0), tcl = -0.5)
})
```

```{r, message = FALSE, echo = FALSE}
library(MPWR)
```

# Introduction

**MPWR** is an R package for multivariate time series (or multivariate 
structured longitudinal data) modeling and optimal segmentation via multiple 
polynomial piecewise regression (MPWR). It uses MLE for the estimation of the 
regression parameters with dynamic programming for the segmentation. This 
document gives a quick tour of **MPWR** (version `r packageVersion("MPWR")`)
functionalities.

It was written in R Markdown, using the [knitr](https://cran.r-project.org/package=knitr)
package for production.

See `help(package="MPWR")` for further details and references provided by
`citation("MPWR")`.

# Load data

```{r}
data("toydataset")
x <- toydataset$x
Y <- as.matrix(toydataset[,c("y1", "y2", "y3")])
```

# Set up MPWR model parameters

```{r}
K <- 5 # Number of segments
p <- 3 # Polynomial degree
```

# Estimation

```{r}
mpwr <- fitMPWRFisher(X = x, Y = Y, K, p)
```

# Summary

```{r}
mpwr$summary()
```

# Plots

## Regressors

```{r}
mpwr$plot(what = "regressors")
```

## Segmentation

```{r}
mpwr$plot(what = "segmentation")
```
